---
title: "Exercise #3"
author: "Philipp Adami (12617871)"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1

### Exercise 1d)


Strengths of github: 1. You can track your progress over time, and recover lost files if needed.
                     2. Great for group projects / collaborations, since everyone can track everyone's progress.
Weaknesses of github: 1. It can be hard and confusing to use at first.
                      2. It cannot handle larger files or data.
  

## Exercise 3

### Exercise 3a)

```{r}
library(tidyverse)
library(readr)
pixar_films <- read_csv("pixar_films.csv")
```

```{r}
pixar_films <- pixar_films %>% filter(!is.na(film))

pixar_films$film_rating <- as.factor(pixar_films$film_rating)

```

The variable "film_rating" maybe categorizes the age-restriction for the film, meaning a "G"-rated movie is good to watch as a kid, while "PG"-rated is not recommended for kids to watch alone (PG may stand for "Parental Guide", while may stand for "General").
It is appropriate to have "film_rating" as a factor variable, since there are only limited (PG and G, maybe a few more) categorical possibilities for entries (so discrete categories).


### Exercise 3b)

```{r}
pixar_series <- data.frame(
  series_name = c("Toy Story", "Toy Story", "Toy Story", "Toy Story", "Cars", "Cars", "Cars", "Incredibles", "Incredibles", "Finding", "Finding "),
  film = c("Toy Story", "Toy Story 2", "Toy Story 3", "Toy Story 4", "Cars", "Cars 2", "Cars 3", "The Incredibles", "Incredibles 2", "Finding Nemo", "Finding Dory"),
  nr_of_movies = c(4, 4, 4, 4, 3, 3, 3, 2, 2, 2, 2)
)

view(pixar_series)
write.csv(pixar_series, "pixar_series.csv", row.names = FALSE)

```


### Exercise 3c) 

```{r}
public_response <- read_csv("public_response.csv")

public_response$cinema_score <- as.factor(public_response$cinema_score)

public_response$cinema_score <- factor(public_response$cinema_score,
                                       levels = c("A-", "A", "A+"))

```

```{r}
pixar_newfilms <- left_join(pixar_films, public_response, by = "film")
```

### Aufgabe 3d)


```{r}
pixar_helpdf <- left_join(pixar_series, public_response, by = "film")
```
A help-dataframe to help me with the following plot.

```{r}
ggplot(
  data = pixar_helpdf,
  mapping = aes(
    x = film,
    y = metacritic,
    
    
  )
) + geom_col() + 
  labs(
    x = "Filmtitle",
    y = "Moviescore by metacritic",
    title = "Moviescore of Pixar-filmseries"
  )
```

I'm noticing that the first movie of a series is always rated the best, and the later the movie in the series, the worse it gets percieved by critics.

## Exercise 4 

### Exercise 4a+b+c)

```{r}
alcohol <- read_csv("Alcohol consumption since 1890 (Alexander & Holmes, 2017).csv")
```

Dataset Name: Alcohol consumption since 1890 (Alexander & Holmes, 2017)
Link: https://github.com/owid/owid-datasets/tree/master/datasets/Alcohol%20consumption%20by%20type%20since%201890%20(Alexander%20%26%20Holmes%2C%202017)

### Exercise 4d)

My scientific question is: How did alcohol-consume change over the last 130 years? And in what countries is it the highest over the years?
This is an interesting question, since society has changed dramatically in the last 130 years, so it's interesting to see how one of the most popular addictions have changed along the way.

### Exercise 4e)

```{r}
alcohol %>% group_by(Year) %>% summarize(Alcohol_consumtion = mean(`Alcohol consumption since 1890 (Alexander & Holmes, 2017)`)) 
```

```{r}
alcohol %>% group_by(Entity) %>% summarize(Alcohol_consumtion = mean(`Alcohol consumption since 1890 (Alexander & Holmes, 2017)`))
```

In the first table, you can see the development of alcohol consumption in the years 1890, 1920, 1960, 1970, 1980, 1999, 2000 and 2014, and you can clearly see that the average consumption per year has been going down.This is probably due to the fact that population has grown, so the average per capita alcohol consumption has shrunk. 

In the second plot, you can see the average alcohol consumption per capita in select high-income countries. The highest consumption is from France, with 14.5 liters per capita, while the lowest are Japan and Finland with only 5.8 and 5.1 liters per capita.


### Exercise 4f)

```{r, fig.cap = "Alcohol consumption per capita in some years from 1890 to 2014"}
ggplot(
  data = alcohol,
  mapping  = aes(
    x = Year,
    y = `Alcohol consumption since 1890 (Alexander & Holmes, 2017)`
  )
) + geom_col()

```



