---
title: "Exercise #3"
author: "Philipp Adami (12617871)"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1

### Exercise 1d)


Strengths of github: 1. You can track your progress over time, and recover lost files if needed.
                     2. Great for group projects / collaborations, since everyone can track everyone's progress.
Weaknesses of github: 1. It can be hard and confusing to use at first.
                      2. It cannot handle larger files or data.
  

## Exercise 3

### Exercise 3a)

```{r}
library(tidyverse)
library(readr)
pixar_films <- read_csv("pixar_films.csv")
```

```{r}
pixar_films <- pixar_films %>% filter(!is.na(film))

pixar_films$film_rating <- as.factor(pixar_films$film_rating)

```

The variable "film_rating" maybe categorizes the age-restriction for the film, meaning a "G"-rated movie is good to watch as a kid, while "PG"-rated is not recommended for kids to watch alone (PG may stand for "Parental Guide", while may stand for "General").
It is appropriate to have "film_rating" as a factor variable, since there are only limited (PG and G, maybe a few more) categorical possibilities for entries (so discrete categories).


### Exercise 3b)

```{r}
pixar_series <- data.frame(
  series_name = c("Toy Story", "Cars", "Incredibles", "Finding Nemo"),
  nr_of_movies = c(4, 3, 2, 2)
)
```






