---
title: "Exercise #3"
author: "Philipp Adami (12617871)"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1

### Exercise 1d)


Strengths of github: 1. You can track your progress over time, and recover lost files if needed.
                     2. Great for group projects / collaborations, since everyone can track everyone's progress.
Weaknesses of github: 1. It can be hard and confusing to use at first.
                      2. It cannot handle larger files or data.
  

## Exercise 3

### Exercise 3a)

```{r}
library(tidyverse)
library(readr)
pixar_films <- read_csv("pixar_films.csv")
```

```{r}
pixar_films <- pixar_films %>% filter(!is.na(film))

pixar_films$film_rating <- as.factor(pixar_films$film_rating)

```

The variable "film_rating" maybe categorizes the age-restriction for the film, meaning a "G"-rated movie is good to watch as a kid, while "PG"-rated is not recommended for kids to watch alone (PG may stand for "Parental Guide", while may stand for "General").
It is appropriate to have "film_rating" as a factor variable, since there are only limited (PG and G, maybe a few more) categorical possibilities for entries (so discrete categories).


### Exercise 3b)

```{r}
pixar_series <- data.frame(
  series_name = c("Toy Story", "Toy Story", "Toy Story", "Toy Story", "Cars", "Cars", "Cars", "Incredibles", "Incredibles", "Finding", "Finding "),
  film = c("Toy Story", "Toy Story 2", "Toy Story 3", "Toy Story 4", "Cars", "Cars 2", "Cars 3", "The Incredibles", "Incredibles 2", "Finding Nemo", "Finding Dory"),
  nr_of_movies = c(4, 4, 4, 4, 3, 3, 3, 2, 2, 2, 2)
)

view(pixar_series)
write.csv(pixar_series, "pixar_series.csv", row.names = FALSE)

```


### Exercise 3c) 

```{r}
public_response <- read_csv("public_response.csv")

public_response$cinema_score <- as.factor(public_response$cinema_score)

public_response$cinema_score <- factor(public_response$cinema_score,
                                       levels = c("A-", "A", "A+"))

```

```{r}
pixar_newfilms <- left_join(pixar_films, public_response, by = "film")
```

### Aufgabe 3d)


```{r}
pixar_helpdf <- left_join(pixar_series, public_response, by = "film")
```
A help-dataframe to help me with the following plot.

```{r}
ggplot(
  data = pixar_helpdf,
  mapping = aes(
    x = film,
    y = metacritic,
    
    
  )
) + geom_col() + 
  labs(
    x = "Filmtitle",
    y = "Moviescore by metacritic",
    title = "Moviescore of Pixar-filmseries"
  )
```

I'm noticing that the first movie of a series is always rated the best, and the later the movie in the series, the worse it gets percieved by critics.

## Exercise 4 

### Exercise 4a+b+c)

```{r}
alcohol <- read_csv("Alcohol consumption since 1890 (Alexander & Holmes, 2017).csv")
```

Dataset Name: Alcohol consumption since 1890 (Alexander & Holmes, 2017)
Link: https://github.com/owid/owid-datasets/tree/master/datasets/Alcohol%20consumption%20by%20type%20since%201890%20(Alexander%20%26%20Holmes%2C%202017)

### Exercise 4d)

My scientific question is: How did alcohol-consume change over the last 60 years? (To be concrete, how did it change from 1960 to 2014 in the given countries)
This is an interesting question, since society has changed dramatically in the last 60 years, so it's interesting to see how one of the most popular addictions have changed along the way.




